### 2013-11-23 proposal/proposal/chapter2.tex
changes

        \subsection{Cooperative Game Examples}\label{sec:CWSDefinition}

@@

        In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
        DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
        users and services to maximize their gain. A two-player
        non-cooperative game between web services and community master was
        introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
        game-theoretic model, the strategies available to a web service
        when facing a new community are requesting to join the community,
        accepting the master's invitation to join the community, or
        refusing the invitation to join. The set of strategies for
        communities are inviting the web service or refusing the web
        service's join request. Based on their capacity, market share and
        reputation, the two players have different set of utilities over
        the strategy profiles of the game. The main limits of this game
        model are: 1) its consideration of only three quality parameters,
        while the other factors are simply ignored; and 2) the
        non-consideration of the web services already residing within the
        community. The game is only between the community master and the
        new web service, and the inputs from all the other members are
        simply ignored. The consideration of those inputs is a significant
        issue as existing web services can lose utility or payoff because
        of the new member, which can results in an unhealthy and unstable
        group. The problem comes from the fact that the existing members
        should collaborate with the new web services, so probably their
        performance as a group can suffer. Existing members may even
        deviate and try to join other communities if they are unsatisfied.
        Those considerations of forming stable and efficient coalitions
        are the main contributions of our paper.

>>>>

        \subsection{Examples on Cooperative Game Solution Concepts}\label{sec:CWSDefinition}

@@

        In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
        DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
        users and services to maximize their gain. A two-player
        non-cooperative game between web services and community master was
        introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
        game-theoretic model, the strategies available to a web service
        when facing a new community are requesting to join the community,
        accepting the master's invitation to join the community, or
        refusing the invitation to join. The set of strategies for
        communities are inviting the web service or refusing the web
        service's join request. Based on their capacity, market share and
        reputation, the two players have different set of utilities over
        the strategy profiles of the game. The main limits of this game
        model are: 1) its consideration of only three quality parameters,
        while the other factors are simply ignored; and 2) the
        non-consideration of the web services already residing within the
        community. The game is only between the community master and the
        new web service, and the inputs from all the other members are
        simply ignored. The consideration of those inputs is a significant
        issue as existing web services can lose utility or payoff because
        of the new member, which can results in an unhealthy and unstable
        group. The problem comes from the fact that the existing members
        should collaborate with the new web services, so probably their
        performance as a group can suffer. Existing members may even
        deviate and try to join other communities if they are unsatisfied.
        Those considerations of forming stable and efficient coalitions
        are the main contributions of this research work.
